Class-based network segregation, Economic Inequality and Redistributive Preferences across societies

### 2024-04-15 paper1_jiturra.Rmd
Update paper1_jiturra.Rmd

>>>>

## Income inequalty groups

```{r table1-ineq-groups, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

dfreg <- na.omit(dfreg)
tab_countries<- 
  dfreg %>% 
  group_by(country3) %>% 
  summarise(gini_disp=mean(gini_disp)) %>% 
  mutate(gini_q05=ntile(gini_disp,5),
         gini_d10=ntile(gini_disp,10)) %>% as.data.frame() %>% 
  arrange(gini_d10) %>% 
  dplyr::select(-gini_disp)

dfreg <- dfreg %>% left_join(tab_countries,by="country3")

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------

library(estimatr)

# Quintile 1 (low)
digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==1),weights = WEIGHT)
digclas1_VW_Q1_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
digclas1_VW_Q1_2 <- update(digclas1_VW_Q1_1, . ~ . +dclass3res_V*homclass3_V_res)

# Quintile 2 (mid-low)
digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion+ factor(country2),data=subset(dfreg,gini_q05==2),weights = WEIGHT)
digclas1_VW_Q2_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
digclas1_VW_Q2_2 <- update(digclas1_VW_Q2_1, . ~ . +dclass3res_V*homclass3_V_res)

# Quintile 3 (middle)
digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==3),weights = WEIGHT)
digclas1_VW_Q03_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
digclas1_VW_Q03_2 <- update(digclas1_VW_Q03_1, . ~ . +dclass3res_V*homclass3_V_res)

# Quintile 4 (middle-high)
digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==4),weights = WEIGHT)
digclas1_VW_Q04_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
digclas1_VW_Q04_2 <- update(digclas1_VW_Q04_1, . ~ . +dclass3res_V*homclass3_V_res)

# Quintile 5 (high)
digclas1_VW_1<- lm(egal~1 + homclass3_V_res +know_total+socialtrust +female+agenum+age2 + partner + religion + factor(country2),data=subset(dfreg,gini_q05==5),weights = WEIGHT)
digclas1_VW_Q05_1 <- update(digclas1_VW_1, . ~ . + dclass3res_V+female+agenum+age2+edyears+ Q03pcm+workst+union+dclass3spo_V)
digclas1_VW_Q05_2<- update(digclas1_VW_Q05_1, . ~ . +dclass3res_V*homclass3_V_res)

digclas1_Q05 <- 
list(digclas1_VW_Q1_1,digclas1_VW_Q1_2,digclas1_VW_Q2_1,digclas1_VW_Q2_2,
     digclas1_VW_Q03_1,digclas1_VW_Q03_2,digclas1_VW_Q04_1,digclas1_VW_Q04_2,
     digclas1_VW_Q05_1,digclas1_VW_Q05_2)

header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       symbol = "+",scalebox = 0.60,
      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
      custom.gof.rows = list("Country FE"=rep("Yes",10)),
      # include.loglik = FALSE,include.aic = FALSE,
      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
       float.pos = "h!",
      # file = "table1.html"
       use.packages = F)
```

```{r fig1-marg-ineqgrup, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
marginal <- bind_rows(
plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
marginal$quintile <- factor(marginal$quintile,labels = c("Q1","Q2","Q3","Q4","Q5"))

ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
  geom_point(size=2) + 
  geom_errorbar(width=.2)+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0,color="red") +
  facet_grid(~quintile) +
  labs(x=NULL,y="Redistributive preferences")  
```
